---
title: "Tar_Flux_Bioko_Maps"
author: "Daniel T. Citron"
date: "12/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries}
library(data.table)
library(rgdal, quietly = TRUE)
library(ggplot2)
library(MASS)
library(rgeos)
library(latex2exp)
```


# Generate Figures
In this document, we will generate figures and maps of Bioko Island as an applied example of the Ross-Macdonald model results

We will not do the basic data processing here, but we will generate the figures and compute R0 based on input files generated elsewhere:

## Import data
```{r Import data, echo=FALSE}
setwd("/Users/dtcitron/Documents/Publications/TarFlux")

# Reading in the data structures for creating Bioko Island maps:
bioko <- readOGR("Data/BI_maps/bioko", "bioko_admin1")
areas_inh <- readOGR("Data/BI_maps/areas_inh", "areas_inh")
areasf <- fortify(areas_inh, region = "areaId")
# Some more maps, outlining the 6 on-island destination regions
ad2 <- rgdal::readOGR("Data/BI_maps/ad2EG/ad2_eg.shp")
ad2 <- subset(ad2, admin2 %in% c("Malabo", "Riaba", "Luba", "Baney"))
ad4 <- rgdal::readOGR("Data/BI_maps/admin4shp/admin4V19.shp")
ad4.sub <- subset(ad4, admin4 %in% c("Ureka", "Moka Malabo"))

# area.data <- fread("Data/BI_maps/areadata.csv") # this is basic survey data, might want to delete later...

# Reading in the fitted travel model results
# The fitted travel model results come from the multinomial fit for the Spatial Uncertainty project
travel.model.data <- fread(file = "Data/RM_figures_data.csv")
# fwrite(travel.model.data[,.(areaId, ad2, malabo, pop, prall_map, pre_map,
#                      prt_map, prt_map.freq,
#                      p.off, p.ban, p.lub, p.mal, p.mok, p.ria, p.ure)],
#        file = "Data/RM_figures_data.csv")

```

## Define Parameters for Ross-Macdonald Model
These we use to compute the expressions for R0, once we know PR values and the Time at Risk matrix:
```{r Ross-Macdonald parameters}
a = 0.3*0.9
b = 0.55
c = 0.15
r = 1./200 # rate at which people become cured
eta = 1./30 # rate at which prophylaxis wears off
p = 0.9 # fraction of surviving mosquitoes
g = 1 - p # fraction of dying mosquitoes
peip = p^11 # fraction of mosquitoes who survive incubation period


# Travel duration, fit using the 2018 data set
trip.duration.eg <- 1/0.04713604 # rate of return from mainland eg to bioko
trip.duration.bi <- 1/0.09670302 # rate of return from trips on bioko
```


## Prevalence and population values
```{r Prevalence and Population Surfaces}
PR <- travel.model.data$prall_map
H <- travel.model.data$pop

## Total population
pop.total <- sum(travel.model.data$pop)#  225950
## Set Baseline populations in each Area 
# Baseline Populations in each Area
pop.inputs <- rep(0, 194 + 1)
pop.inputs[1:194] <- travel.model.data$pop 
# assume Bata's population is the same as Malabo's
pop.inputs[194+1] <- sum(travel.model.data[ad2=="Malabo" | ad2 == "Peri" ]$pop)
```



## Time at Risk model R0 calculation
First, need to calculate the Time at Risk matrix:
```{r Time at Risk matrix calculation - Part 1}
# Matrix of probabilities of travel destination
holder <- as.matrix(travel.model.data[, c("p.off", "p.ban", "p.lub", "p.mal", "p.mok", "p.ria", "p.ure")])


# Transform to weight travel probabilities by time at destination
for (i in 1:194){
  holder[i,] <- holder[i,]*c(trip.duration.eg,rep(trip.duration.bi,6))
}
```


```{r Time at Risk destination disambiguation}
## Define mat.weighted, which we will use to transform the Time at Risk matrix as mapping travel from
# areaId -> ad2 
areaIds <- sort(unique(travel.model.data$areaId))

## Set up weighted travel ####
mat.weighted <- matrix(0, nrow = 7, ncol = 195)
# off-island travel
mat.weighted[1,195] <- 1
# baney
mat.weighted[2, which(areaIds %in% travel.model.data[ad2=="Baney"]$areaId)] <- travel.model.data[ad2=="Baney"]$pop/sum(travel.model.data[ad2=="Baney"]$pop)
# luba
mat.weighted[3, which(areaIds %in% travel.model.data[ad2=="Luba"]$areaId)] <- travel.model.data[ad2=="Luba"]$pop/sum(travel.model.data[ad2=="Luba"]$pop)
# malabo
mat.weighted[4, which(areaIds %in% travel.model.data[ad2=="Malabo" | ad2=="Peri"]$areaId)] <- travel.model.data[ad2=="Malabo" | ad2=="Peri"]$pop/sum(travel.model.data[ad2=="Malabo" | ad2=="Peri"]$pop)
# moka
mat.weighted[5, which(areaIds %in% travel.model.data[ad2=="Moka"]$areaId)] <- travel.model.data[ad2=="Moka"]$pop/sum(travel.model.data[ad2=="Moka"]$pop)
# riaba
mat.weighted[6, which(areaIds %in% travel.model.data[ad2=="Riaba"]$areaId)] <- travel.model.data[ad2=="Riaba"]$pop/sum(travel.model.data[ad2=="Riaba"]$pop)
# ureka
mat.weighted[7, which(areaIds %in% travel.model.data[ad2=="Ureka"]$areaId)] <- travel.model.data[ad2=="Ureka"]$pop/sum(travel.model.data[ad2=="Ureka"]$pop)

# Disambiguate travel destination 
weighted.travel.probabilities <- as.matrix(holder) %*% mat.weighted
```

```{r Time at Risk matrix calculation, part 2}
TaR.disambiguated <- diag(1, nrow = 195, ncol = 195)
for (i in 1:194){
  TaR.disambiguated[i,] <- weighted.travel.probabilities[i, ]/(sum(weighted.travel.probabilities[i, ]) + travel.model.data$prt_map.freq[i]^(-1))
  TaR.disambiguated[i,i] <- 1 + TaR.disambiguated[i,i] - sum(weighted.travel.probabilities[i, ]/(sum(weighted.travel.probabilities[i, ]) + travel.model.data$prt_map.freq[i]^(-1)))
  #   The extra term (here) accounts for the fact that we would otherwise be double-subtracting the probability weight of traveling to one's own map-area
}
```


Now, we can use the Time at Risk matrix and the PR surface to solve for R0:
```{r Time at Risk R0}
# PfPR, with off-island PR = .43 # From Ncogo et al, and from MAP
pfpr.input <- c(travel.model.data$prall_map, .43)
# Calculate Kappa, the force of infection from humans to mosquitoes, using the Time at Risk matrix
kappa <- as.vector(pop.inputs[1:195]*pfpr.input[1:195]) %*% TaR.disambiguated / (as.vector(pop.inputs[1:195]) %*% TaR.disambiguated)
# Borrowing notation from Ruktanonchai et al.
d.vec <- (b*c*kappa/(1 + a*c*kappa/g))
d.x.mat <- matrix(0, nrow = 195, ncol = 195);
for (i in 1:195){
  d.x.mat[i,i] = d.vec[i]
}
g.x <- r*pfpr.input/(1 - pfpr.input)
# Calculate Vectorial Capacity by inverting the Time at Risk matrix
VC.tar <- ginv(TaR.disambiguated %*% d.x.mat) %*% as.vector(g.x)
# Calculate Time at Risk R0 from vectorial capacity
R0.tar <- VC.tar[1:195]*b*c/r

#hist(R0.tar[1:194], breaks = seq(0,2,.1), freq = TRUE)
```

## Flux model R0 calculation
We can calculate the flux model's coefficients from the Time at Risk model
```{r Flux model R0}
tau.travel.times <- c(rep(trip.duration.bi, 194), trip.duration.eg)

# Flux volume matrix:
M.flux.volume = matrix(0, nrow = 195, ncol = 195)
for (i in 1:195){
  for (j in 1:195){
    M.flux.volume[i,j] = TaR.disambiguated[i,j]*pop.inputs[i]/tau.travel.times[j] +
                         TaR.disambiguated[j,i]*pop.inputs[j]/tau.travel.times[i]
  }
  M.flux.volume[i,i] <- 0
}
# Flux rate matrix 
# divide the ith row, corresponding to starting at the ith location, with the ith pop.star.flux.denom:
M.flux.rate = matrix(0, nrow = 195, ncol = 195)
for (i in 1:195){
  M.flux.rate[i,] <- M.flux.volume[i,]/pop.inputs[i]  
  M.flux.rate[i,i] <- 0
}

# Calculate the number of infected individuals at each site
i.infected = pfpr.input * pop.inputs

# Calculate the net flux out of *infected* individuals (different from all individuals, because pfpr is different everywhere)
# This is the added input for the R0 calculation
net.flux.infected <- rep(0, 195)
for (i in 1:195){
  net.flux.infected[i] <- - sum(M.flux.rate[i,])*i.infected[i] + (t(M.flux.rate) %*% i.infected)[i]
  # - (infected people who are leaving) + (infected people who are entering)
}

# Calculate kappa, for the flux model; which only requires local pfpr measurements
kappa <- pfpr.input[1:195]
# Borrowing notation from Ruktanonchai et al.
d.vec <- (b*c*kappa/(1 + a*c*kappa/g))
g.x.flux <- t((r*pfpr.input- net.flux.infected/pop.inputs)/(1 - (pfpr.input)))
# Calculate Vectorial Capacity by inverting the Time at Risk matrix
VC.flux <- g.x.flux/d.vec
# Calculate Time at Risk R0 from vectorial capacity
R0.flux <- VC.flux[1:195]*b*c/r

#hist(R0.flux[1:194], breaks = seq(-70,10,.1), freq = TRUE)
```

```{r Histograms, for comparison}
# Write out the histogram-related data; for making a beautiful histogram in the accompanying python notebook
hist.flux = data.table(model = "Flux", R0 = R0.flux[1:194])#.squeeze[1:194])
hist.tar = data.table(model = "TaR", R0 = R0.tar[1:194])#.squeeze[1:194])
#fwrite(rbind(hist.flux, hist.tar), "/Users/dtcitron/Documents/Publications/TarFlux/Data/R0_BI_histo_data.csv")

ggplot() +
 geom_histogram(data = hist.flux,aes(R0), fill = "Red", alpha = 0.5, bins = 100) +
 geom_histogram(data = hist.tar,aes(R0), fill = "Blue", alpha = 0.5, bins = 100)

```

## Generate Visualizations
```{r Discretize R0 distribution for controlling the color gradients}
# discretize R0 distribution, for controlling color gradient
R0.tar.discrete <- rep(0, 194)
# R0.tar.discrete[which(R0.tar[1:194] < .825)] <- 0
# R0.tar.discrete[which(R0.tar[1:194] > .825 & R0.tar[1:194] < .875)] <- 1
# R0.tar.discrete[which(R0.tar[1:194] > .875 & R0.tar[1:194] < .925)] <- 2
# R0.tar.discrete[which(R0.tar[1:194] > .925 & R0.tar[1:194] < .975)] <- 3
# R0.tar.discrete[which(R0.tar[1:194] > .975 & R0.tar[1:194] < 1.025)] <- 4
# R0.tar.discrete[which(R0.tar[1:194] > 1.025 & R0.tar[1:194] < 1.075)] <- 5
# R0.tar.discrete[which(R0.tar[1:194] > 1.075 & R0.tar[1:194] < 1.125)] <- 6
# R0.tar.discrete[which(R0.tar[1:194] > 1.125 & R0.tar[1:194] < 1.175)] <- 7
# R0.tar.discrete[which(R0.tar[1:194] > 1.175)] <- 8
R0.tar.discrete[which(R0.tar[1:194] < .65)] <- 0
R0.tar.discrete[which(R0.tar[1:194] > .65 & R0.tar[1:194] < .75)] <- 1
R0.tar.discrete[which(R0.tar[1:194] > .75 & R0.tar[1:194] < .85)] <- 2
R0.tar.discrete[which(R0.tar[1:194] > .85 & R0.tar[1:194] < .95)] <- 3
R0.tar.discrete[which(R0.tar[1:194] > .95 & R0.tar[1:194] < 1.05)] <- 4
R0.tar.discrete[which(R0.tar[1:194] > 1.05 & R0.tar[1:194] < 1.15)] <- 5
R0.tar.discrete[which(R0.tar[1:194] > 1.15 & R0.tar[1:194] < 1.25)] <- 6
R0.tar.discrete[which(R0.tar[1:194] > 1.25 & R0.tar[1:194] < 1.35)] <- 7
R0.tar.discrete[which(R0.tar[1:194] > 1.35)] <- 8

R0.flux.squeeze <- rep(0, 194)
R0.flux.squeeze[which(R0.flux[1:194] < 0)] = -1
R0.flux.squeeze[which(R0.flux[1:194] > 0. & R0.flux[1:194] < 0.5)] = 0
R0.flux.squeeze[which(R0.flux[1:194] > 0.5 & R0.flux[1:194] < 1)] = 1
R0.flux.squeeze[which(R0.flux[1:194] > 1 & R0.flux[1:194] < 1.5)] = 2
R0.flux.squeeze[which(R0.flux[1:194] > 1.5 & R0.flux[1:194] < 2.)] = 3
R0.flux.squeeze[which(R0.flux[1:194] > 2 & R0.flux[1:194] < 2.5)] = 4
R0.flux.squeeze[which(R0.flux[1:194] > 2.5 & R0.flux[1:194] < 3)] = 5
R0.flux.squeeze[which(R0.flux[1:194] > 3)] = 6
#R0.flux.squeeze[which(R0.flux[1:194] > 3.5 )] = 7
```

Prepare data for plotting
```{r Prepare Data for plotting }
plot.data <- merge(travel.model.data, data.table(areaId = areaIds, 
                                                 R0.tar = R0.tar[1:194],
                                                 R0.tar.discrete = R0.tar.discrete,
                                                 R0.flux = R0.flux[1:194],
                                                 R0.flux.squeeze = R0.flux.squeeze), by = "areaId")
plot.data = merge(areasf, plot.data, by.x = "id", by.y = "areaId", all=TRUE)

# Here's where we generate the template for making island plots
p1 = ggplot(data = plot.data, aes(x=long, y=lat, group = group))
p2 = p1 + geom_polygon(data = bioko, aes(x = long, y = lat, group = group), 
                       color = "black", fill="grey", size = 0.25)
p3 = p2 + geom_path(data = ad2) + geom_path(data = ad4.sub)
```


Time at Risk model R0 map - continuous levels
```{r Time at Risk R0 Discrete Scale}
map <- p3 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = R0.tar), color = NA, size = 0.25) +
  scale_fill_gradient(name="R0, TaR", low="#D1EFFF", high="#0000D6", limits=c(0,2)) +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),axis.title.y=element_blank(), panel.background=element_blank(), 
        legend.position=c(0.2, 0.75), legend.key.size = unit(12, "mm"), 
        legend.title = element_text(size = 20),
        legend.text=element_text(size=18))
map
```

Time at Risk model R0 map - with discretized color levels for clarity
```{r Time at Risk R0 Continuous Scale}
map <- p3 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = factor(R0.tar.discrete)), 
                         color = NA, size = 0.25) +
  # scale_fill_gradient(name = "R0",
  #                     low = "#D1EFFF", high = "#0000D6",
  #                     breaks = c(2, 4, 6), labels = c("0.9", "1", "1.1")) + 
  scale_fill_manual(name = TeX("$R_{0,ST}"),
                    breaks = c(8, 7, 6, 5, 4, 3, 2, 1, 0),
                    values = c("#E5F6FF",
                               "#C5E4F9",
                               "#A6CDF4",
                               "#86B2EF",
                               "#6994EA",
                               "#4E73E5",
                               "#314EE0",
                               "#1828DB",
                               "#0000D6"),
                    labels = c(expression("≥1.35"), "", expression("1.25"), "", expression("1.0"), "",expression("0.75"), "", expression("≤0.65")),
                    guide = "legend") +
geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),axis.title.y=element_blank(), panel.background=element_blank(), 
        legend.position=c(0.175, 0.73), legend.key.size = unit(8, "mm"),#legend.key.size = unit(12, "mm"), 
        legend.title = element_text(size = 28),
        legend.text=element_text(size=22))
map
# Save this map as a PDF, 7x7in
```

Flux model R0 map, with a continuous scale
```{r R0 Flux Continuous}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = R0.flux), color = NA, size = 0.25) +
  scale_fill_gradient(name="R0 with flux model", low="yellow", high="red", limits=c(0,4)) +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8))
map
```


Flux model R0 map, with discretized color levels for clarity
```{r R0 Flux Discrete}
map <- p3 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = factor(R0.flux.squeeze)), 
                         color = NA, size = 0.25) +
  scale_fill_manual(name = TeX("$R_{0,Flux}"),
                    breaks = c(6, 5, 4, 3, 2, 1, 0,-1),
                    values = c("#575655",
                               "#EAFF00",
                               "#EAD700", #EDDA00", 
                               "#EFAF00", #F0B600", 
                               "#F28500", #F66D00", 
                               "#F75A00", #F94800", 
                               "#FC2E00", #FC2400", 
                               "#FF0000"),
                    labels = c(expression("≥ 3.0"), " ", "2.0", " ", "1.0", " ", "0.0", expression("≤ 0")),
                    guide = "legend") +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
    theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),axis.title.y=element_blank(), panel.background=element_blank(), 
          legend.position=c(0.175, .74), legend.key.size = unit(8, "mm"),#legend.key.size = unit(12, "mm"), 
          legend.title = element_text(size = 28),
          legend.text=element_text(size=22))
map
# Save this map as a PDF, 7x7in
```

# Prevalence Map
```{r R0 Flux Discrete}
map <- p3 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = prall_map), 
                         color = NA, size = 0.25) +
  scale_fill_gradient(name="PR",
                      low="yellow", high="red", limits=c(0, .4)) +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
    theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),axis.title.y=element_blank(), panel.background=element_blank(), 
          legend.position=c(0.2, 0.75), legend.key.size = unit(10, "mm"),#legend.key.size = unit(12, "mm"), 
          legend.title = element_text(size = 28),
          legend.text=element_text(size=22))
map
# Save this map as a PDF, 7x7in
```

# Leaving Home Frequency Map
```{r}
require(viridis)
map <- p3 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = prt_map), 
                         color = NA, size = 0.25) +
  scale_fill_viridis(name="P(Travel)", limits=c(0, .5)) +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
    theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),axis.title.y=element_blank(), panel.background=element_blank(), 
          legend.position=c(0.2, 0.75), legend.key.size = unit(10, "mm"),#legend.key.size = unit(12, "mm"), 
          legend.title = element_text(size = 28),
          legend.text=element_text(size=22))
map
```


# Travel patterns maps
First: find and plot a map of Ad2 + Moka + Ureka?
Second: Find the centroids of the different regions
Third: Plot arrows weighted by destination choice?

What are the centroids of these locations?
```{r}
dest.xy <- rbind(data.table(ad2 = "Malabo", as.data.table(gCentroid(subset(ad2, admin2 == "Malabo")))),
  data.table(ad2 = "Baney", as.data.table(gCentroid(subset(ad2, admin2 == "Baney")))),
  data.table(ad2 = "Luba", as.data.table(gCentroid(subset(ad2, admin2 == "Luba")))),
  data.table(ad2 = "Riaba", as.data.table(gCentroid(subset(ad2, admin2 == "Riaba")))),
  data.table(ad2 = "Ureka", as.data.table(gCentroid(subset(ad4, admin4 == "Ureka")))),
  data.table(ad2 = "Moka", as.data.table(gCentroid(subset(ad4, admin4 == "Moka Malabo"))))
)
# Move the centroid of Malabo and for Luba to the northwest, simply for visualization purposes
dest.xy[ad2 == "Baney"]$x <- 485916
dest.xy[ad2 == "Baney"]$y <- 410037.2 # aimed at 582
dest.xy[ad2 == "Malabo"]$x <- 467997.0
dest.xy[ad2 == "Malabo"]$y <- 410756.0
dest.xy[ad2 == "Luba"]$x <- 452948.6
dest.xy[ad2 == "Luba"]$y <- 383201.2 # aimed below 2083
dest.xy <- rbind(dest.xy, data.table(ad2 = "EG", x = 500000, y = 374834.3))
```


Now we need to figure out the eights on each of these arrows
```{r}
dest.xy$weight.335 = unlist(travel.model.data[areaId == 335, .(p.mal, p.ban, p.lub, p.ria, p.ure, p.mok, p.off)])
dest.xy$weight.1175 = unlist(travel.model.data[areaId == 1175, .(p.mal, p.ban, p.lub, p.ria, p.ure, p.mok, p.off)])
dest.xy$weight.2496 = unlist(travel.model.data[areaId == 2496, .(p.mal, p.ban, p.lub, p.ria, p.ure, p.mok, p.off)])
dest.xy$weight.2694 = unlist(travel.model.data[areaId == 2694, .(p.mal, p.ban, p.lub, p.ria, p.ure, p.mok, p.off)])
```

What are the centroids of location 335, or 2694?
```{r}
centroids <- rgdal::readOGR("Data/BI_maps/mapArea_centroids/mapareagrid_centroids.shp")
centroids <- data.table(areaId = centroids$OBJECTID,# this is the same as areaId
                        coordinates(centroids)) # lat-long coordinates of the centroids
centroids[areaId %in% c(335, 1175, 2496, 2694)]
```


```{r}
map.335 <- p2 + 
  geom_path(data = ad2) +
  geom_path(data = ad4.sub) + 
  #geom_point(data = dest.xy, mapping = aes(x = x, y = y, group = NA)) +
  geom_curve(aes(x = centroids[areaId == 335]$coords.x1, y = centroids[areaId == 335]$coords.x2, xend = x, yend = y, group = NA, size = weight.335/2), 
             data = dest.xy, 
             arrow = arrow(length = unit(0.05, "npc")),
             curvature = .1) +
  geom_polygon(data = plot.data[plot.data$id == "335",], aes(x = long, y = lat, group = group, fill = factor(R0.tar.discrete)), color = NA, size = 10) +
  scale_fill_manual(values = c("#B6D1F9")) + 
  theme(aspect.ratio = 1, 
        panel.background = element_rect(fill = "white", colour = "white"),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")
map.335
```
```{r}
map.1175 <- p2 + 
  geom_path(data = ad2) +
  geom_path(data = ad4.sub) + 
  #geom_point(data = dest.xy, mapping = aes(x = x, y = y, group = NA)) +
  geom_curve(aes(x = centroids[areaId == 1175]$coords.x1, y = centroids[areaId == 1175]$coords.x2, xend = x, yend = y, group = NA, size = weight.1175/2), 
             data = dest.xy, 
             arrow = arrow(length = unit(0.05, "npc")),
             curvature = .1) +
  geom_polygon(data = plot.data[plot.data$id == "1175",], aes(x = long, y = lat, group = group, fill = factor(R0.tar.discrete)), color = NA, size = 10) +
  scale_fill_manual(values = c("#B6D1F9")) + 
  theme(aspect.ratio = 1, 
        panel.background = element_rect(fill = "white", colour = "white"),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")
map.1175
```

```{r}
map.2496 <- p2 + 
  geom_path(data = ad2) +
  geom_path(data = ad4.sub) + 
  #geom_point(data = dest.xy, mapping = aes(x = x, y = y, group = NA)) +
  geom_curve(aes(x = centroids[areaId == 2496]$coords.x1, y = centroids[areaId == 2496]$coords.x2, xend = x, yend = y, group = NA, size = weight.2496/2), 
             data = dest.xy, 
             arrow = arrow(length = unit(0.05, "npc")),
             curvature = .1) +
  geom_polygon(data = plot.data[plot.data$id == "2496",], aes(x = long, y = lat, group = group, fill = factor(R0.tar.discrete)), color = NA, size = 10) +
  scale_fill_manual(values = c("#B6D1F9")) + 
  theme(aspect.ratio = 1, 
        panel.background = element_rect(fill = "white", colour = "white"),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")
map.2496
```

```{r}
map.2694 <- p2 + 
  geom_path(data = ad2) +
  geom_path(data = ad4.sub) + 
  geom_curve(aes(x = 473923.2, y = 374253.2, xend = x, yend = y, group = NA, size = weight.2694/2), 
             data = dest.xy, 
             arrow = arrow(type = "open", length = unit(0.05, "npc")),
             curvature = .1) +
  geom_polygon(data = plot.data[plot.data$id == "2694",], aes(x = long, y = lat, group = group, fill = factor(R0.tar.discrete)), color = NA, size = 10) +
  scale_fill_manual(values = c("#B6D1F9")) + 
  theme(aspect.ratio = 1, 
        panel.background = element_rect(fill = "white", colour = "white"),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")
map.2694
```

